### 2014-07-10 writeups/context-dependence.tex
Some questions for @petrelharp.
This shows the depth of my ignorance. :)

I'd like to better understand how you are approaching likelihood
calculation that has some per-site component but also a nontrivial
motif component. For example, in the CpG model, mutations can arise
because of the "usual" per-nucleotide mutation, or arise because of the
actual CpG motif mutation as you describe. Do we think of this as being
a model with m=1 and l=1? If that's the case then we have many
overlapping motifs, and so then do we only calculate the likelihood for
part of the data via nonoverlapping windows? Or

@@

If we use only a subset of patterns $\{(x_k,y_k)\}$ chosen so that $\E[M_1(x,y) M_{k+1}(x,y)]$ is small (or zero),
the entire collection $\{N(x_k,y_k)\}$ will be close to independent Poisson.
(using Stein's method)
Then we'll have the correct likelihood function for (this subset of) data.

>>>>

\todo[inline]{In this section I believe that we are talking about the full likelihood, rather than the likelihood of just non-overlapping windows of the data.
I'm also a little confused about "choosing" a subset of patterns.
These pattern choices are determining our model?}

@@

If we use only a subset of patterns $\{(x_k,y_k)\}$ chosen so that $\E[M_1(x,y) M_{k+1}(x,y)]$ is small (or zero),
\todo{M not defined, but I'm guessing that this is effectively saying that the probability of having two different patterns apply to the same sequences is small?}
the entire collection $\{N(x_k,y_k)\}$ will be close to independent Poisson.
(using Stein's method)
Then we'll have the correct likelihood function for (this subset of) data.
